---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

library(ggplot2)
library(dplyr)
library(gridExtra)

official <- c(6.6, 5.6, 5.6, 5.3, 4.6, 4.3, 4.0, 4.2, 5.7, 5.8,
        5.7, 5.3, 4.7, 4.6, 5.0, 7.8, 9.8, 9.1, 8.3, 8.0,
        6.6, 5.7, 4.9, 4.8, 4.4, 4.0) / 100
real <- c(11.8, 10.2, 9.8, 9.4, 8.4, 7.7, 7.1, 7.3, 9.5, 10.0,
          9.9, 9.3, 8.4, 8.4, 9.2, 14.2, 16.7, 16.2, 15.2, 14.5,
          12.7, 11.3, 9.9, 9.4, 8.2, 8.1) /100

unemployment <- data.frame(
  Year = c(c(1994:2019), c(1994:2019)),
  Rate = c(official, real),
  Type = c(rep(times = 26, "official"), rep(times = 26, "real"))
)
p <- ggplot(data = unemployment, aes(x = Year, y = Rate, group = Type)) +
  geom_line(aes(color = Type)) +
  geom_point(aes(color = Type)) +
  theme(legend.position="bottom") +
  xlim (1994, 2019) + scale_y_continuous(labels = scales::percent)

grid.arrange(p + coord_cartesian(xlim = c(1995, 2018)) + ggtitle("Unemployment rate in USA"),
             ncol = 1)


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
